NFC and burnout in teachers - A replication and extension study

### 2021-11-29 Manuscript/Manuscript.Rmd
set figure width

```{r objective1_plot, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r objective1years_plot, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r objective2_plot, echo=FALSE, message=FALSE, warning=FALSE}

>>>>

```{r objective1_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}

@@

```{r objective1years_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}

@@

```{r objective2_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
